Compare pseqs

### 2019-10-04 comparepseqs.Rmd
Typo

for (key in names(rds)) {
    pseq <- import_filter_data(rds[[key]],
                               included = c("MEN", "BL_AGE", "SYSTM", "DIASM", "BMI",
                                            "CURR_SMOKE", "BL_USE_RX_C09",
                                            "Q57X", "BL_USE_RX_C03",
                                            "BL_USE_RX_C07", "BL_USE_RX_C08"))

    bray.dist.m.species <- calculate.beta.matrix(pseq)

>>>>

for (key in names(rds)) {
    pseq.species <- import_filter_data(rds[[key]],
                               included = c("MEN", "BL_AGE", "SYSTM", "DIASM", "BMI",
                                            "CURR_SMOKE", "BL_USE_RX_C09",
                                            "Q57X", "BL_USE_RX_C03",
                                            "BL_USE_RX_C07", "BL_USE_RX_C08"))

    bray.dist.m.species <- calculate.beta.matrix(pseq.species)
